Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-15 Report/article.tex
rap

\subsection{Intial set-up cost}
Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.

>>>>

\subsection{Intial set-up cost}
(Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold).\\
Here we estimate the performance in terms of run time for KeyGen, Encrypt, Decrypt, Add, Mult, Recrypt.
